Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-11-26 journal-draft/ettdoc_JG.tex
in ettdoc_JG, change the font of words as normal

\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$N$ is the total number of CR users in network $\mathcal{N}$.
$y_i$ and $x_{ij}$ are binary variables.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.

>>>>

\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$N$ is the total number of CR users in network $\mathcal{N}$.
$y_i$ and $x_{ij}$ are binary variables.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.
